Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-16 analysis/paper/paper.qmd
add DOI

The entire R code [@core2021team] and data files used for all the analysis and visualizations contained in this paper is openly available at https://osf.io/dqna8/ to enable re-use of materials and improve reproducibility and transparency [@marwick2017computational]. All of the figures, tables, statistical test results presented here in addition to the raw data can be independently reproduced with the code and data in this repository. The code is released under the MIT license, the data as CC-0, and figures as CC-BY, to enable maximum re-use.

>>>>

The entire R code [@core2021team] and data files used for all the analysis and visualizations contained in this paper is openly available at DOI: 10.17605/OSF.IO/DQNA8 to enable re-use of materials and improve reproducibility and transparency [@marwick2017computational]. All of the figures, tables, statistical test results presented here in addition to the raw data can be independently reproduced with the code and data in this repository. The code is released under the MIT license, the data as CC-0, and figures as CC-BY, to enable maximum re-use.
